The Driving Forces of API Evolution

### 2015-06-03 thesis/paper.tex
removed newpages
review first half

\newpage
\section{Introduction} \label{introduction}
%API Design background
As the software industry and the open-source movement continue to grow, the number of public Application Programming Interfaces (APIs) is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}. The main reason being that API users are required to update their application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. 
%Software Evolution background
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

@@

\newpage
%Structure ofpaper
The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study and introduce the case company and their API. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the implications of our work. In Section \ref{conclusion} summarise the study and give suggestions for future work that builds on our research.

\section{Background} \label{background}
This section will introduce the fields of API design, software evolution and it will provide a review of studies that are related to our study. The subsequent section will introduce the case company with a description of the API used in this study.

@@

%RQ2
To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.

@@

\newpage
\section{Results} \label{results}

@@

%Lehman Intro
Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} are present in the API. 
A summary of our findings can be seen in Table \ref{table:lehman}. 
The evidence found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System mainly relate to enhancive changes that add functionality to the API. 
It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality. The only law which was found to have little effect in the evolution of the API analysed in this study was the law of Conservation of Organisational Stability. Our results rather show the opposite, that the work rate is variant.

@@

@@

\newpage
\smallskip \noindent
\textbf{Reductive  }
%Definition
Reductive changes are defined as changes that remove or reduce functionality. This is distinctive from a deprecation as reductive types of change remove functionality completely.
%Data & Explanation
Only a single reductive type of change was identified. This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user. Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}. It was revealed during the interview that the functionality was removed because the company A no longer wished to support this feature. 
%Conclusion
As this was the only reductive change found, we conclude that the evolution of the API was not primarily driven by reductive changes.

>>>>

\section{Introduction} \label{introduction}
%API Design background
As the software industry and the open-source movement continue to grow, the number of public Application Programming Interfaces (APIs) is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, henning2007api, mcdonnell2013empirical, robbes2012developers}. The main reason being that API users are required to update their application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. 
%Software Evolution background
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

@@

 \newpage
%Structure ofpaper
The sections following the Introduction are structured as follows: In Section \ref{background}, we present the background and previously published work that is related to our study and introduce the case company and their API. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented and in Section \ref{discussion}, we discuss the implications of our work. In Section \ref{conclusion} we summarise the study and give suggestions for future work that builds on our research.

\section{Background} \label{background}
This section will introduce the fields of APIs, software evolution and it will provide a review of studies that are related to our study. The subsequent section will introduce the case company with a description of the API used in this study.

@@

\newpage
%RQ2
To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by calculating Cohen's kappa \cite{cohen1968weighted} for the gathered data.

@@

\section{Results} \label{results}

@@

@@

%Lehman Intro
Our analysis of the results related to \textbf{RQ1} showed that seven out of the eight of Lehman's laws \cite{lehman90sview} are present in the API. 
A summary of our findings can be seen in Table \ref{table:lehman}. 
The evidence found for the laws of Continuing Change, Self Regulation, Conservation of Familiarity, Continuing Growth and Feedback System mainly relate to enhancive changes that add functionality to the API. 
It was also found that the laws of Increasing Complexity and Declining Quality do apply, but that the changes which support these laws usually had a secondary intent related to complexity or quality. The only law which was found to have little effect in the evolution of the API analysed in this study was the law of Conservation of Organisational Stability.

@@

\smallskip \noindent
\textbf{Reductive  }
%Definition
Reductive changes are defined as changes that remove or reduce functionality. This is distinctive from a deprecation as reductive types of change remove functionality completely.
%Data & Explanation
Only a single reductive type of change was identified. This reductive change removed functionality that provided the ability to buffer individual images for closer analysis by a user. Given that it is more common to refactor APIs and not remove functionality \cite{dig2005role, xing2006refactoring}. It was revealed during the interview that the functionality was removed because the company A no longer wished to support this feature. 
%Conclusion
As this was the only reductive change found, we conclude that the evolution of the API was not primarily driven by reductive changes.
